### 2021-10-13 paper/output/document/paper41.tex
added philosophical upshot

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Logical Background%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
an inability to fully represent the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence. In this interpretation, 
a subject is merely defined as ``that which can act." It does not include any other properties, such as 
rationality or dignity. As I will show, for the purposes of defining the universalizability test, this 
``thin" representation of a subject suffices.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model the 
substitution operator.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

@@

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Constructing the Formalization%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
an inability to fully represent the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence. In this interpretation, 
a subject is merely defined as ``that which can act." It does not include any other properties, such as 
rationality or dignity. As I will show, for the purposes of defining the universalizability test, this 
``thin" representation of a subject suffices.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model the 
substitution operator.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

\isadelimdocument
\endisadelimdocument
\isatagdocument
\isamarkupsubsection{Application Tests%
}
\isamarkuptrue%
\endisatagdocument
{\isafolddocument}%
\isadelimdocument
\endisadelimdocument
As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
I specify particular maxims as constants with no properties and gradually add properties to understand 
how the system handles different kinds of maxims. For example, initially I simply define ``murder'' as 
a constant $M$, and then I specify properties of murder, such as murder is not universalizable or 
murder is prohibited.%
\isacommand{consts}\isamarkupfalse%
\ M{\isacharcolon}{\isacharcolon}os\isanewline
\isamarkupcmt{The constant $M$ will represent the act ``murder."%
\isamarkupcmt{Should I represent this as a set of maxims? should I specify the circumstances and goals?%

@@

%:%449=318%:%
%:%461=320%:%
%:%462=321%:%
%:%463=322%:%
%:%464=323%:%
%:%465=324%:%
%:%466=325%:%
%:%468=327%:%
%:%469=327%:%
%:%471=328%:%
%:%472=328%:%
%:%474=329%:%
%:%475=329%:%

### 2021-10-13 paper/output/document/threeflags.tex
added philosophical upshot

%
\begin{isabellebody}%
\setisabellecontext{threeflags}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
$\textbf{Choice to Formalize the FUL}$

In \emph{Groundwork of the Metaphysics of Morals}, Kant presents three formulations, or versions, 
of what he calls the ``supreme law of morality." I will focus on the first of these three formulations, 
and below I explain the formulations and defend my choice.

@@

Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
argument is disputed \cite{sepkant}, for those who believe it, the
stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
lends the exact same power as a formalization of the second or third formulation of the categorical 
imperative. In fact, future work could formalize the other formulas and try to prove that they 
are identical. Kant believes that his argument for the equality of the formulas is analytical, and
if he is correct, it should be possible to recreate the argument in logic.

$\textbf{Definition of a Maxim}$

The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
below and consider an additional component that Kitcher argues for.

$\emph{O'Niell's Original Schematic and The Role of Practical Judgement}$

O'Neill $\cite[37]{actingonprinciple}$ presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
view that a maxim is a circumstance, act, goal tuple. A maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed, which are often referred to as ``morally relevant circumstances."

@@

While this may appear to be a weakness of my system, I believe that it actually
allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers presents 
the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics \cite{powers}.}
Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
about the properties of rational wills. In fact, Korsgaard argues that morality derives its authority over us, 
or normativity, only because is it a property of a rational will, and we, as human beings, are rational wills.
If ethics is meant to guide human behavior, the role of the computer becomes clear as not a replacement for our will,
but instead as a tool to help guide our wills and reason more efficiently 
and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
of this issue.

$\emph{Exclusion of Motive}$

Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim \cite{whatisamaxim}. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.

$\textbf{Practical Contradiction Interpretation}$

Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
she believes that the text partially supports this interpretation, her argument is philosophical and 
derives its strength from the plausibility of the practical contradiction interpretation.

@@

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%19=9%:%
%:%20=10%:%
%:%21=11%:%
%:%22=12%:%
%:%23=13%:%
%:%24=14%:%
%:%25=15%:%
%:%26=16%:%
%:%27=17%:%
%:%28=18%:%
%:%29=19%:%
%:%30=20%:%
%:%31=21%:%
%:%32=22%:%
%:%33=23%:%
%:%34=24%:%
%:%35=25%:%
%:%36=26%:%
%:%37=27%:%
%:%38=28%:%
%:%39=29%:%
%:%40=30%:%
%:%41=31%:%
%:%42=32%:%
%:%43=33%:%
%:%44=34%:%
%:%45=35%:%
%:%46=36%:%
%:%47=37%:%
%:%48=38%:%
%:%49=39%:%
%:%50=40%:%
%:%51=41%:%
%:%52=42%:%
%:%53=43%:%
%:%54=44%:%
%:%55=45%:%
%:%56=46%:%
%:%57=47%:%
%:%58=48%:%
%:%59=49%:%
%:%60=50%:%
%:%61=51%:%
%:%62=52%:%
%:%63=53%:%
%:%64=54%:%
%:%65=55%:%
%:%66=56%:%
%:%67=57%:%
%:%68=58%:%
%:%69=59%:%
%:%70=60%:%
%:%71=61%:%
%:%72=62%:%
%:%73=63%:%
%:%74=64%:%
%:%75=65%:%
%:%76=66%:%
%:%77=67%:%
%:%78=68%:%
%:%79=69%:%
%:%80=70%:%
%:%81=71%:%
%:%82=72%:%
%:%83=73%:%
%:%84=74%:%
%:%85=75%:%
%:%86=76%:%
%:%87=77%:%
%:%88=78%:%
%:%89=79%:%
%:%90=80%:%
%:%91=81%:%
%:%92=82%:%
%:%93=83%:%
%:%94=84%:%
%:%95=85%:%
%:%96=86%:%
%:%97=87%:%
%:%98=88%:%
%:%99=89%:%
%:%100=90%:%
%:%101=91%:%
%:%102=92%:%
%:%103=93%:%
%:%104=94%:%
%:%105=95%:%
%:%106=96%:%
%:%107=97%:%
%:%108=98%:%
%:%109=99%:%
%:%110=100%:%
%:%111=101%:%
%:%112=102%:%
%:%113=103%:%
%:%114=104%:%
%:%115=105%:%
%:%116=106%:%
%:%117=107%:%
%:%118=108%:%
%:%119=109%:%
%:%120=110%:%
%:%121=111%:%
%:%122=112%:%
%:%123=113%:%
%:%124=114%:%
%:%125=115%:%
%:%126=116%:%
%:%127=117%:%
%:%128=118%:%
%:%129=119%:%
%:%130=120%:%
%:%131=121%:%
%:%132=122%:%
%:%133=123%:%
%:%134=124%:%
%:%135=125%:%
%:%136=126%:%
%:%137=127%:%
%:%138=128%:%
%:%139=129%:%
%:%140=130%:%
%:%141=131%:%
%:%142=132%:%
%:%143=133%:%
%:%144=134%:%
%:%145=135%:%
%:%146=136%:%
%:%147=137%:%
%:%148=138%:%
%:%149=139%:%
%:%150=140%:%
%:%151=141%:%
%:%152=142%:%
%:%153=143%:%
%:%154=144%:%
%:%155=145%:%
%:%156=146%:%
%:%157=147%:%
%:%158=148%:%
%:%159=149%:%
%:%160=150%:%
%:%161=151%:%
%:%162=152%:%
%:%163=153%:%
%:%164=154%:%
%:%165=155%:%
%:%166=156%:%
%:%167=157%:%
%:%168=158%:%
%:%169=159%:%
%:%170=160%:%
%:%171=161%:%
%:%172=162%:%
%:%173=163%:%
%:%174=164%:%
%:%175=165%:%
%:%176=166%:%
%:%177=167%:%
%:%178=168%:%
%:%179=169%:%
%:%180=170%:%
%:%181=171%:%
%:%182=172%:%
%:%183=173%:%
%:%184=174%:%
%:%185=175%:%
%:%186=176%:%
%:%187=177%:%
%:%188=178%:%
%:%189=179%:%
%:%190=180%:%
%:%191=181%:%
%:%192=182%:%
%:%193=183%:%
%:%194=184%:%
%:%195=185%:%
%:%196=186%:%
%:%197=187%:%
%:%198=188%:%
%:%199=189%:%
%:%200=190%:%
%:%201=191%:%
%:%202=192%:%
%:%203=193%:%
%:%204=194%:%
%:%205=195%:%
%:%206=196%:%
%:%207=197%:%
%:%208=198%:%
%:%209=199%:%
%:%210=200%:%
%:%211=201%:%
%:%212=202%:%
%:%213=203%:%
%:%214=204%:%
%:%215=205%:%
%:%216=206%:%
%:%217=207%:%
%:%218=208%:%
%:%219=209%:%
%:%220=210%:%
%:%221=211%:%
%:%222=212%:%
%:%223=213%:%
%:%224=214%:%
%:%225=215%:%
%:%226=216%:%
%:%227=217%:%
%:%228=218%:%
%:%229=219%:%
%:%230=220%:%
%:%231=221%:%
%:%232=222%:%
%:%233=223%:%
%:%234=224%:%
%:%235=225%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{threeflags}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Choice to Formalize the FUL%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In \emph{Groundwork of the Metaphysics of Morals}, Kant presents three formulations, or versions, 
of what he calls the ``supreme law of morality." I will focus on the first of these three formulations, 
and below I explain the formulations and defend my choice.

@@

Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
argument is disputed \cite{sepkant}, for those who believe it, the
stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
lends the exact same power as a formalization of the second or third formulation of the categorical 
imperative. In fact, future work could formalize the other formulas and try to prove that they 
are identical. Kant believes that his argument for the equality of the formulas is analytical, and
if he is correct, it should be possible to recreate the argument in logic.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Definition of a Maxim%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
below and consider an additional component that Kitcher argues for.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{O'Niell's Original Schematic and The Role of Practical Judgement%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
O'Neill $\cite[37]{actingonprinciple}$ presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
view that a maxim is a circumstance, act, goal tuple. A maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed, which are often referred to as ``morally relevant circumstances."

@@

While this may appear to be a weakness of my system, I believe that it actually
allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers presents 
the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics \cite{powers}.}
Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
about the properties of rational wills. In fact, Korsgaard argues that morality derives its authority over us, 
or normativity, only because is it a property of a rational will, and we, as human beings, are rational wills.
If ethics is meant to guide human behavior, the role of the computer becomes clear as not a replacement for our will,
but instead as a tool to help guide our wills and reason more efficiently 
and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
of this issue.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Exclusion of Motive%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim \cite{whatisamaxim}. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Practical Contradiction Interpretation%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
she believes that the text partially supports this interpretation, her argument is philosophical and 
derives its strength from the plausibility of the practical contradiction interpretation.

@@

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%24=9%:%
%:%36=12%:%
%:%37=13%:%
%:%38=14%:%
%:%39=15%:%
%:%40=16%:%
%:%41=17%:%
%:%42=18%:%
%:%43=19%:%
%:%44=20%:%
%:%45=21%:%
%:%46=22%:%
%:%47=23%:%
%:%48=24%:%
%:%49=25%:%
%:%50=26%:%
%:%51=27%:%
%:%52=28%:%
%:%53=29%:%
%:%54=30%:%
%:%55=31%:%
%:%56=32%:%
%:%57=33%:%
%:%58=34%:%
%:%59=35%:%
%:%60=36%:%
%:%61=37%:%
%:%62=38%:%
%:%63=39%:%
%:%64=40%:%
%:%65=41%:%
%:%66=42%:%
%:%67=43%:%
%:%68=44%:%
%:%69=45%:%
%:%70=46%:%
%:%71=47%:%
%:%72=48%:%
%:%73=49%:%
%:%74=50%:%
%:%75=51%:%
%:%76=52%:%
%:%77=53%:%
%:%78=54%:%
%:%79=55%:%
%:%80=56%:%
%:%81=57%:%
%:%82=58%:%
%:%83=59%:%
%:%84=60%:%
%:%85=61%:%
%:%86=62%:%
%:%87=63%:%
%:%88=64%:%
%:%97=66%:%
%:%109=68%:%
%:%110=69%:%
%:%111=70%:%
%:%112=71%:%
%:%113=72%:%
%:%114=73%:%
%:%115=74%:%
%:%116=75%:%
%:%117=76%:%
%:%118=77%:%
%:%119=78%:%
%:%120=79%:%
%:%121=80%:%
%:%122=81%:%
%:%123=82%:%
%:%124=83%:%
%:%125=84%:%
%:%126=85%:%
%:%127=86%:%
%:%128=87%:%
%:%129=88%:%
%:%130=89%:%
%:%139=91%:%
%:%151=93%:%
%:%152=94%:%
%:%153=95%:%
%:%154=96%:%
%:%155=97%:%
%:%156=98%:%
%:%157=99%:%
%:%158=100%:%
%:%159=101%:%
%:%160=102%:%
%:%161=103%:%
%:%162=104%:%
%:%163=105%:%
%:%164=106%:%
%:%165=107%:%
%:%166=108%:%
%:%167=109%:%
%:%168=110%:%
%:%169=111%:%
%:%170=112%:%
%:%171=113%:%
%:%172=114%:%
%:%173=115%:%
%:%174=116%:%
%:%175=117%:%
%:%176=118%:%
%:%177=119%:%
%:%178=120%:%
%:%179=121%:%
%:%180=122%:%
%:%181=123%:%
%:%182=124%:%
%:%183=125%:%
%:%184=126%:%
%:%185=127%:%
%:%186=128%:%
%:%187=129%:%
%:%188=130%:%
%:%189=131%:%
%:%190=132%:%
%:%191=133%:%
%:%192=134%:%
%:%193=135%:%
%:%194=136%:%
%:%195=137%:%
%:%196=138%:%
%:%197=139%:%
%:%198=140%:%
%:%199=141%:%
%:%200=142%:%
%:%201=143%:%
%:%202=144%:%
%:%211=146%:%
%:%223=148%:%
%:%224=149%:%
%:%225=150%:%
%:%226=151%:%
%:%227=152%:%
%:%228=153%:%
%:%229=154%:%
%:%230=155%:%
%:%231=156%:%
%:%232=157%:%
%:%233=158%:%
%:%234=159%:%
%:%235=160%:%
%:%236=161%:%
%:%237=162%:%
%:%238=163%:%
%:%239=164%:%
%:%240=165%:%
%:%241=166%:%
%:%242=167%:%
%:%243=168%:%
%:%244=169%:%
%:%245=170%:%
%:%254=172%:%
%:%266=174%:%
%:%267=175%:%
%:%268=176%:%
%:%269=177%:%
%:%270=178%:%
%:%271=179%:%
%:%272=180%:%
%:%273=181%:%
%:%274=182%:%
%:%275=183%:%
%:%276=184%:%
%:%277=185%:%
%:%278=186%:%
%:%279=187%:%
%:%280=188%:%
%:%281=189%:%
%:%282=190%:%
%:%283=191%:%
%:%284=192%:%
%:%285=193%:%
%:%286=194%:%
%:%287=195%:%
%:%288=196%:%
%:%289=197%:%
%:%290=198%:%
%:%291=199%:%
%:%292=200%:%
%:%293=201%:%
%:%294=202%:%
%:%295=203%:%
%:%296=204%:%
%:%297=205%:%
%:%298=206%:%
%:%299=207%:%
%:%300=208%:%
%:%301=209%:%
%:%302=210%:%
%:%303=211%:%
%:%304=212%:%
%:%305=213%:%
%:%306=214%:%
%:%307=215%:%
%:%308=216%:%
%:%309=217%:%
%:%310=218%:%
%:%311=219%:%
%:%312=220%:%
%:%313=221%:%
%:%314=222%:%
%:%315=223%:%
%:%316=224%:%
%:%317=225%:%
%:%318=226%:%
